DeepTriangle: A Deep Learning Approach to Loss Reserving

### 2019-09-07 manuscript/manuscript.Rmd
typo

In developing our framework, which we call DeepTriangle, we also draw inspiration from the existing stochastic reserving literature. Works that propose utilizing data in addition paid losses include @quarg2004munich, which uses incurred losses, and @miranda2012double, which incorporates claim count information. Moving beyond a single homogeneous portfolio, @avanzi2016stochastic considers the dependencies among lines of business within an insurer's portfolio, and @peremans2018robust proposes a robust general multivariate chain ladder approach to accommodate outliers. There is also a category of models, referred to as state space or adaptive models, that allow parameters to evolve recursively in time as more data is observed [@chukhrova2017state]. This iterative updating mechanism is analogous to the recurrent neural network architecture presented in this paper.

>>>>

In developing our framework, which we call DeepTriangle, we also draw inspiration from the existing stochastic reserving literature. Works that propose utilizing data in addition to paid losses include @quarg2004munich, which uses incurred losses, and @miranda2012double, which incorporates claim count information. Moving beyond a single homogeneous portfolio, @avanzi2016stochastic considers the dependencies among lines of business within an insurer's portfolio, and @peremans2018robust proposes a robust general multivariate chain ladder approach to accommodate outliers. There is also a category of models, referred to as state space or adaptive models, that allow parameters to evolve recursively in time as more data is observed [@chukhrova2017state]. This iterative updating mechanism is analogous to the recurrent neural network architecture presented in this paper.
